\papertitle

### 2021-03-05 source_separation/paper/paper.tex

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the orchestration process. We first discuss the motivation of this addition and its effects on the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assess which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improves, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we compare unsupervised methods to supervised methods in the case of assisted orchestration, where data is relatively scarce.
	\end{abstract}
	%

>>>>

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the computer-assisted orchestration process. We first discuss the motivation of this addition and its effects on the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assess which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improves, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we compare unsupervised methods to supervised methods in the case of assisted orchestration, where data is relatively scarce.
	\end{abstract}
	%
